How to use flowCore package

### 2007-01-29 inst/doc/HowTo-flowCore.Rnw
correct vignette add man page
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@22286 bc3139a8-67e5-0310-9ffc-ced21a209358

<<plotTRansfo,eval=FALSE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(data08Transform,plotParameters=c(1,2))
@

@@

<<plotTRansfo,eval=FALSE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
##we should find a way to specified if an parameters has been transformed 
## either in the title or via the label of the axis 
plot(data08LogTransform,plotParameters=c("FSC-H","SSC-H"),main="Log2 transformed data")
@

@@

<<define and apply rangeGate1,eval=TRUE, echo=FALSE,results=hide>>=
rangeGate <- rectangleGate(filterId="rangeGate","FSC-H"=c(.2,Inf))
b08rangeGate <- filter(b08,rangeGate)
@ 
<<plotTOfilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y="FSC-H", pch="*",main="B08, with debris")
@
<<plotfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08[b08rangeGate],y="FSC-H", pch="*",main="B08, lower debris removed")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotTOfilter} A}
\subfigure{\includegraphics[width=40mm]{plotCenterfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

<<FL1Filtered1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result3,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered2, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result4,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered3, echo=FALSE, eval=FALSE,fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result5,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@

@@

\clearpage
\small{
<<sessionInfo>>=
sessionInfo()
@ 
}
\end{document}

>>>>

<<plotTransfo1,eval=FALSE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
plot(data08Transform,plotParameters=c(1,2))
@

@@

<<plotTransfo2,eval=FALSE, echo=FALSE,fig=TRUE,prefix=FALSE,include=FALSE>>=
##we should find a way to specified if an parameters has been transformed 
## either in the title or via the label of the axis 
plot(data08LogTransform,plotParameters=c("FSC-H","SSC-H"),main="Log2 transformed data")
@

@@

<<define and apply rangeGate1,eval=TRUE, echo=FALSE,results=hide>>=
rangeGate <- rectangleGate(filterId="rangeGate","FSC-H"=c(.2,Inf))
b08rangeGate <- filter(b08,rangeGate)
@ 
<<plotTofilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y="FSC-H", pch="*",main="B08, with debris")
@
<<plotfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08[b08rangeGate],y="FSC-H", pch="*",main="B08, lower debris removed")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotTofilter} A}
\subfigure{\includegraphics[width=40mm]{plotfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

<<FL1Filtered1, echo=FALSE, eval=FALSE,  fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result3,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered2, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result4,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@ 
<<FL1Filtered3, echo=FALSE, eval=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08.result5,parent=b08.result2,plotParameters=c("FSC-H","FL1-H"),
          xlim=c(0,1024),ylim=c(0,1024),pch="*")
@

@@

\clearpage
\bibliographystyle{cyto} 
\bibliography{cytoref}
\clearpage
\small{
<<sessionInfo>>=
sessionInfo()
@ 
}
\end{document}
